Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
another pass on dependency graph

\subsection{\Hydras Genealogy and Dependencies}

@@

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };    
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };
\end{scope}

\begin{scope}[yshift=-0.7cm,xshift=0.25cm]
\node[rectangle, draw=black,dashed,minimum height=0.5cm,minimum width=1.5cm] (equations) { Equations };
\node[rectangle, draw=black,dashed,minimum height=0.5cm,minimum width=1.5cm,right of=equations, node distance=2cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,right of=mathcomp, node distance=2cm] (paramcoq) { Paramcoq };
\end{scope}

@@

\draw[->,dotted] (additions.south) -- (chains.north west) ;
\draw[->] (goedel) -- (goedelcc) ;
\draw[->] (goedel) -- (hydras.north west) ;
\draw[->] (cantor) -- (hydras.north) ;
\draw[->] (cantor.south) -- (gaia.north west) ;
\draw[->] (hydras) -- (gaiahydras) ;
\draw[->] (gaia.south west) -- (gaiahydras) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:round}
\end{figure}

In mainstream software, it is common for packages to continually depend on a large number of packages. In contrast, projects in the Coq ecosystem are often subject to ``dependency aversion'', where maintainers eschew depending on useful packages because it may lead to work in adapting to upstream changes. With \Hydras, we hope to demonstrate that projects with complex dependencies are feasible to manage using recent advances in build management and infrastructure.

>>>>

\subsection{\Hydras Genealogy, Dependencies, and Organization}

@@

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };    
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };
\end{scope}

\begin{scope}[yshift=-0.7cm,xshift=0.25cm]
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (equations) { Equations };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=equations, node distance=2cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=equations, node distance=4.7cm] (paramcoq) { Paramcoq };
\end{scope}

@@

\draw[->,dotted] (additions.south) -- (chains.north) ;
\draw[->,dotted] (goedel) -- (goedelcc) ;
\draw[->,dotted] (goedel) -- (hydras.north west) ;
\draw[->,dotted] (cantor) -- (hydras.north) ;
\draw[->,dotted] (cantor.south) -- (gaia.north west) ;
\draw[->] (hydras) -- (gaiahydras) ;
\draw[->] (gaia.south west) -- (gaiahydras.east) ;

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (equations.south) -- (chains) ;
\draw[->] (paramcoq.south) -- (hydras) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:round}
\end{figure}

In traditional software development, it is common for packages to continually depend on a large number of packages. In contrast, projects in the Coq ecosystem are often subject to ``dependency aversion'', where maintainers eschew depending on useful packages because it may lead to work in adapting to upstream changes. With \Hydras, we hope to demonstrate that projects with complex dependencies are feasible to manage using recent advances in build management and infrastructure.
